---
title: "Bibliometric analysis"
author: "Carlos Carbajal"
date: "1 June 2018"
output:
  html_document:
    self_contained: no
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Bibliometric analysis
Bibliometrics is statistical analysis of written publications, such as books or articles. Citation analysis is a commonly used bibliometric method which is based on constructing the citation graph, a network or graph representation of the citations between documents. Many research fields use bibliometric methods to explore the impact of their field, the impact of a set of researchers, the impact of a particular paper, or to identify particularly impactful papers within a specific field of research. Data from citation indexes can be analyzed to determine the popularity and impact of specific articles, authors, and publications.

This analysis was developed using the package develop for R from Aria, M & Cuccurullo, C:

> Aria, M. & Cuccurullo, C. (2017) bibliometrix: An R-tool for comprehensive science mapping analysis, Journal of Informetrics, 11(4), pp 959-975, Elsevier.

For further information regarding this package visit http://www.bibliometrix.org.

## Initialization
To develop the analysis, R requires the use of the bibliometrix package.
```{r initiallisation, message = FALSE}
# Loading the required libraries
require(bibliometrix, quietly = TRUE)
```
The next step is to load the dataset obtained either from WoS Clarative analytics or Scopus databases. The bibliometrix package offers functions to import files from `*.txt` or `*.bib` files using the function `readFiles()`. Then, the loaded data needs to be structured into a dataframe using the function `convert2df()`. 
```{r load dataset, eval = FALSE, message = FALSE}
# Importing data from WoS-export
bm <- readFiles("1_data/wos-digital_innovation-2000-2018.bib")
# Structuring data as a dataframe
bm <- convert2df(bm, dbsource = "isi", format = "bibtex")
```
```{r load Rdata, include=FALSE}
load(file = "2_blackbox/1_bm.Rdata")
rownames(bm) <- bm$SR
```
## Bibliometric analysis
The next step is to analyse the data to extract and relate the citation information, using the function `biblioAnalysis()` the dataset is analysed. Then, a summary of the bibliography is presented using the function `summary()`.
```{r bibliometric analysis, }
# blibliometric analysis
bm_anl <- biblioAnalysis(bm, sep = "; ") # It is necesary to identify the separator character used by the database.
# Printing bibliometric summary
bm_smm <- summary(object = bm_anl, k = 12) # k represents the number of entries shown in the summary
```

