---
title: "Bibliometric analysis"
author: "Carlos Carbajal"
date: "1 June 2018"
output:
  html_document:
    self_contained: no
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Bibliometric analysis
Bibliometrics is statistical analysis of written publications, such as books or articles. Citation analysis is a commonly used bibliometric method which is based on constructing the citation graph, a network or graph representation of the citations between documents. Many research fields use bibliometric methods to explore the impact of their field, the impact of a set of researchers, the impact of a particular paper, or to identify particularly impactful papers within a specific field of research. Data from citation indexes can be analyzed to determine the popularity and impact of specific articles, authors, and publications.

This analysis was developed using the package develop for R from Aria, M & Cuccurullo, C:

> Aria, M. & Cuccurullo, C. (2017) bibliometrix: An R-tool for comprehensive science mapping analysis, Journal of Informetrics, 11(4), pp 959-975, Elsevier.

For further information regarding this package visit http://www.bibliometrix.org.

## Initialization
To develop the analysis, R requires the use of the bibliometrix package.
```{r initiallisation, message = FALSE}
# Loading the required libraries
require(bibliometrix, quietly = TRUE)
```
The next step is to load the dataset obtained either from WoS Clarative analytics or Scopus databases. The bibliometrix package offers functions to import files from `*.txt` or `*.bib` files using the function `readFiles()`. Then, the loaded data needs to be structured into a dataframe using the function `convert2df()`. 
```{r load dataset, eval = FALSE, message = FALSE}
# Importing data from WoS-export
bm <- readFiles("1_data/wos-digital_innovation-2000-2018.bib")
# Structuring data as a dataframe
bm <- convert2df(bm, dbsource = "isi", format = "bibtex")
```
```{r load Rdata, include=FALSE}
load(file = "2_blackbox/1_bm.Rdata")
rownames(bm) <- bm$SR
```
## Bibliometric analysis
The next step is to analyse the data to extract and relate the citation information, using the function `biblioAnalysis()` the dataset is analysed. Then, a summary of the bibliography is presented using the function `summary()`.
```{r bibliometric analysis}
# blibliometric analysis
bm_anl <- biblioAnalysis(bm, sep = "; ") # It is necesary to identify the separator character used by the database.
# Printing bibliometric summary
bm_smm <- summary(object = bm_anl, k = 12) # k represents the number of entries shown in the summary
```

```{r bibliometric plots, fig.show = hold, out.width="1600px", out.height="1600px", fig.width=7}
plot(x = bm_anl, k = 12, pause = FALSE)
```

```{r global citations}
# Obtaining most cited references by article and author 
# bm$CR[3] # Used to define the appropriated separatord fiels
bm_cit_art <- citations(M = bm, field = "article", sep = "; ")
head(bm_cit_art$Cited, n = 12)
bm_cit_aut <- citations(M = bm, field = "author", sep = "; ")
head(bm_cit_aut$Cited, n = 12)
```

```{r local citations}
# Obtaining the most cited local references
bm_cit_loc <- localCitations(M = bm,  sep = "; ")
## By Article
head(bm_cit_loc$Papers, n = 12)
## By Author
head(bm_cit_loc$Authors, n = 12)
```

```{r dominance}
# Calculating authors dominance factor
bm_dom <- dominance(results = bm_anl, k = 12)
bm_dom
```

```{r h-index}
# Calculating the authors h-index
## One author: Yoo Youngjin
bm_hin_yoo <- Hindex(M = bm, authors = "YOO Y", sep = ";", years = 10)
bm_hin_yoo$H
bm_hin_yoo$CitationList
## One author: Yoo Youngjin
bm_hin_nam <- Hindex(M = bm, authors = "NAMBISAN S", sep = ";", years = 10)
bm_hin_nam$H
bm_hin_nam$CitationList
## The 12 most productive authors
authors <- gsub(pattern = ",", replacement = " ", x = names(bm_anl$Authors)[1:12]) # Extracting the 12 most productive authors
bm_hin <- Hindex(M = bm, authors = authors, sep = ";", years = 10)
bm_hin$H
bm_hin$CitationList
```

```{r lotkas coefficient, out.width="1600px", out.height="1600px"}
# Estimation of the Lotkas Law coefficient
bm_ltk <- lotka(bm_anl)
bm_ltk$AuthorProd
## Estimation coefficients
bm_ltk$Beta # beta
bm_ltk$C # constant
bm_ltk$R2 # Goodness of fit
bm_ltk$p.value # P-value of K-S two sample test
## Distribution comparison plot
bm_ltk_obs <- bm_ltk$AuthorProd[,3] # Observed distribution
bm_ltk_the <- 10^(log10(bm_ltk$C)-2*log10(bm_ltk$AuthorProd[,1])) # Theoretical distribution
plot(x = bm_ltk$AuthorProd[,1], y = bm_ltk_the, col = "red",
     type = "l", ylim = c(0,1), 
     main = "Scientific Productivity",
     xlab = "Articles", ylab = "Frequency of authors") 
lines(x = bm_ltk$AuthorProd[,1], y = bm_ltk_obs, col = "blue")
legend(x = "topright",  lty = c(1,1,1), cex = 1, bty = "n",
       c("Theoretical (B=2)", "Observed"), col = c("red", "blue"))

```

```{r bibliometric matrices}
#names(bm)
#bm$SO[3] # Used to define the appropriated separatord fiels
## Printing the 12 most productive articles
bm_cma_jou <- cocMatrix(M = bm, Field = "SO", sep = ";")
sort(Matrix::colSums(bm_cma_jou), decreasing = TRUE)[1:12]
## Printing the 12 most productive authors
bm_cma_aut <- cocMatrix(M = bm, Field = "AU", sep = ";")
sort(Matrix::colSums(bm_cma_aut), decreasing = TRUE)[1:12] # Printing the 12 most productive articles
## Printing the 12 most productive universities
bm_cma_uni <- cocMatrix(M = bm, Field = "AU_UN", sep = ";")
sort(Matrix::colSums(bm_cma_uni), decreasing = TRUE)[1:12] # Printing the 12 most productive articles
## Printing the 12 most productive first author country
bm <- metaTagExtraction(M = bm, Field = "AU_CO", sep = ";")
bm_cma_cou <- cocMatrix(M = bm, Field = "AU_CO", sep = ";")
sort(Matrix::colSums(bm_cma_cou), decreasing = TRUE)[1:12] # Printing the 12 most productive articles
## Printing the 12 most cited references
bm_cma_ctr <- cocMatrix(M = bm, Field = "CR", sep = ";")
sort(Matrix::colSums(bm_cma_ctr), decreasing = TRUE)[1:12] # Printing the 12 most productive articles
## Printing the 12 most cited first author
bm <- metaTagExtraction(M = bm, Field = "CR_AU", sep = ";")
bm_cma_cau <- cocMatrix(M = bm, Field = "CR_AU", sep = ";")
sort(Matrix::colSums(bm_cma_cau), decreasing = TRUE)[1:12] # Printing the 12 most productive articles
## Printing the 12 most cited publication
bm <- metaTagExtraction(M = bm, Field = "CR_SO", sep = ";")
bm_cma_cjo <- cocMatrix(M = bm, Field = "CR_SO", sep = ";")
sort(Matrix::colSums(bm_cma_cjo), decreasing = TRUE)[1:12] # Printing the 12 most productive articles
## Printing the 12 most used author's keyword
bm_cma_akw <- cocMatrix(M = bm, Field = "DE", sep = ";")
sort(Matrix::colSums(bm_cma_akw), decreasing = TRUE)[1:12] # Printing the 12 most productive articles
## Printing the 12 most used database aggregator's keyword
bm_cma_dkw <- cocMatrix(M = bm, Field = "ID", sep = ";")
sort(Matrix::colSums(bm_cma_dkw), decreasing = TRUE)[1:12] # Printing the 12 most productive articles
## Printing the 12 most used database aggregator's subject category
bm_cma_dsc <- cocMatrix(M = bm, Field = "SC", sep = ";")
sort(Matrix::colSums(bm_cma_dsc), decreasing = TRUE)[1:12] # Printing the 12 most productive articles
```

```{r coupling, out.width="1600px", out.height="1600px"}
## Coupling articles
bm_bcp_art <- biblioNetwork(M = bm, analysis = "coupling", network = "references", ";")
set.seed(69)
networkPlot(NetMatrix = bm_bcp_art, normalize = "salton",
            weighted = TRUE, n = 20, Title = "Article's coupuling",
            labelsize = 0.5, 
            type = "fruchterman", size = TRUE, remove.multiple = TRUE, edgesize = 5) 
## Coupuling authors
bm_bcp_aut <- biblioNetwork(M = bm, analysis = "coupling", network = "authors", ";")
set.seed(69)
networkPlot(NetMatrix = bm_bcp_aut, normalize = "salton",
            weighted = TRUE, n = 20, Title = "Author's coupuling",
            labelsize = 0.5, 
            type = "fruchterman", size = TRUE, remove.multiple = TRUE)
## Coupuling journals
bm_bcp_jou <- biblioNetwork(M = bm, analysis = "coupling", network = "sources", ";")
set.seed(69)
networkPlot(NetMatrix = bm_bcp_jou, normalize = "salton",
            weighted = TRUE, n = 20, Title = "Journal's coupuling",
            labelsize = 0.5, 
            type = "fruchterman", size = TRUE, remove.multiple = TRUE)
## Coupuling countries
bm_bcp_cou <- biblioNetwork(M = bm, analysis = "coupling", network = "countries", ";")
set.seed(69)
networkPlot(NetMatrix = bm_bcp_cou, normalize = "salton",
            weighted = TRUE, n = 20, Title = "Country's coupuling",
            type = "fruchterman", size = TRUE, remove.multiple = TRUE, labelsize = 0.5)
```

```{r co-citation, out.width="1600px", out.height="1600px"}
## Co-citation articles
bm_bcc_art <- biblioNetwork(M = bm, analysis = "co-citation", network = "references", ";")
set.seed(69)
networkPlot(NetMatrix = bm_bcc_art, n = 30, Title = "Article's co-citation network",
            type = "fruchterman", size = TRUE, remove.multiple = TRUE, 
            labelsize = 0.5, edgesize = 2)
## Co-citation authors
bm_bcc_aut <- biblioNetwork(M = bm, analysis = "co-citation", network = "authors", ";")
set.seed(69)
networkPlot(NetMatrix = bm_bcc_aut, n = 20, Title = "Author's co-citation network",
            type = "fruchterman", size = TRUE, remove.multiple = TRUE, 
            labelsize = 0.5, edgesize = 2)
## Co-citation journals
bm_bcc_jou <- biblioNetwork(M = bm, analysis = "co-citation", network = "sources", ";")
set.seed(69)
networkPlot(NetMatrix = bm_bcc_jou, n = 20, Title = "Author's co-citation network",
            type = "fruchterman", size = TRUE, remove.multiple = TRUE, 
            labelsize = 0.5, edgesize = 2)
```

```{r collaborations, out.width="1600px", out.height="1600px"}
# Author's collaboration
bm_bcl_aut <- biblioNetwork(M = bm, analysis = "collaboration", network = "authors", ";")
set.seed(69)
networkPlot(NetMatrix = bm_bcl_aut, n = dim(bm_bcl_aut)[1], Title = "Author's collaboration",
            type = "kamada", size = TRUE, labelsize = 0.5, edgesize = 2,
            remove.multiple = TRUE, remove.isolates = TRUE, degree = 5)
# University's collaboration
bm_bcl_uni <- biblioNetwork(M = bm, analysis = "collaboration", network = "universities", ";")
set.seed(69)
networkPlot(NetMatrix = bm_bcl_uni, n = dim(bm_bcl_uni)[1], Title = "University's collaboration",
            type = "kamada", size = TRUE, labelsize = 0.5, edgesize = 2,
            remove.multiple = TRUE, remove.isolates = TRUE, degree = 5)
# Country's collaboration
bm_bcl_cou <- biblioNetwork(M = bm, analysis = "collaboration", network = "countries", ";")
set.seed(69)
networkPlot(NetMatrix = bm_bcl_cou, n = dim(bm_bcl_cou)[1], Title = "University's collaboration",
            type = "kamada", size = TRUE, labelsize = 0.5, edgesize = 2,
            remove.multiple = TRUE, remove.isolates = TRUE)
```

```{r co-occurrences, out.width="1600px", out.height="1600px"}
## Aggregator's keywords
bm_coc_dkw <- biblioNetwork(M = bm, analysis = "co-occurrences", network = "keywords", ";")
set.seed(69)
networkPlot(NetMatrix = bm_coc_dkw, normalize = "association", weighted = TRUE, n = 30,
            Title = "Aggregators's keywords co-ocurrences",
            remove.multiple = TRUE, remove.isolates = TRUE, halo = TRUE,
            type = "fruchterman", size = TRUE, labelsize = 0.5, edgesize = 5)
## Authors's keywords
bm_coc_akw <- biblioNetwork(M = bm, analysis = "co-occurrences", network = "author_keywords", ";")
set.seed(69)
networkPlot(NetMatrix = bm_coc_akw, normalize = "association", weighted = TRUE, n = 30,
            Title = "Author's keywords co-ocurrences",
            remove.multiple = TRUE, remove.isolates = TRUE, halo = TRUE,
            curved = FALSE, cluster = "walktrap",
            type = "fruchterman", size = TRUE, labelsize = 0.5, edgesize = 3)
## Subject category
### masking the subject category under  author's keywords
bm2 <- bm
index.akw <- which(names(bm2) == "DE")
index.sc <- which(names(bm2) == "SC")
names(bm2)[index.akw] <- "DE2"
names(bm2)[index.sc] <- "DE"
### masked extraction
bm_coc_sc <- biblioNetwork(M = bm2, analysis = "co-occurrences", network = "author_keywords", ";")
set.seed(70)
networkPlot(NetMatrix = bm_coc_sc, normalize = "association", weighted = TRUE, n = 40,
            Title = "Subject categories's co-ocurrences",
            remove.multiple = TRUE, remove.isolates = TRUE, halo = TRUE,
            curved = FALSE, cluster = "walktrap",
            type = "fruchterman", size = TRUE, labelsize = 0.5, edgesize = 5)
```

```{r co-word, fig.show='hold', out.width="1600px", out.height="1600px"}
bm_cst <- conceptualStructure(M = bm, field = "TI",
                              method = "MCA", stemming = TRUE,
                              labelsize = 6, documents = 15)

```

```{r historical co-citation, out.width="1600px", out.height="1600px"}
bm_hcc <- histNetwork(M = bm, n = 20, sep = ";")
set.seed(5)
histPlot(histResults = bm_hcc, size = FALSE,
         remove.isolates = TRUE,
         label = TRUE, arrowsize = 0.5, labelsize = 0.5)
```