---
title: "Bibliometric analysis"
author: "Carlos Carbajal"
date: "1 June 2018"
output:
  html_document:
    self_contained: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Bibliometric analysis
Bibliometrics is statistical analysis of written publications, such as books or articles. Citation analysis is a commonly used bibliometric method which is based on constructing the citation graph, a network or graph representation of the citations between documents. Many research fields use bibliometric methods to explore the impact of their field, the impact of a set of researchers, the impact of a particular paper, or to identify particularly impactful papers within a specific field of research. Data from citation indexes can be analyzed to determine the popularity and impact of specific articles, authors, and publications.

This analysis was developed using the package develop for R from Aria, M & Cuccurullo, C:

  Aria, M. & Cuccurullo, C. (2017) bibliometrix: An R-tool for comprehensive science mapping analysis, Journal of
  Informetrics, 11(4), pp 959-975, Elsevier.

For further information regarding this package visit http://www.bibliometrix.org.

```{r initiallisation}
summary(cars)
```
